\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Mention KeJia in the conclusion

Aligning the upper part of the ontology on {\sc OpenCyc} (as done by other
knowledge representation systems, like {\sc KnowRob}~\cite{Tenorth2009a} or PEIS
K\&R~\cite{Daoutis2009}) has multiple advantages. First the design of this part
of the ontology is generally difficult: it pertains to abstract concepts whose
mutual relations comes to philosophical debates. The upper taxonomy of {\sc
OpenCyc} represents a relative consensus, at least within the semantic Web
community. Then, because it is a well established project with numerous links to
other on-line databases (like Wikipedia or WordNet), the reuse of key {\sc
OpenCyc} concepts ensures that the knowledge stored by the robot can be shared
or extended with well-defined semantics. The concept of \emph{Object} represents
a typical case of ambiguous meaning: in everyday conversation, an object is a
relatively small physical thing, that can be typically manipulated. A human is
not usually considered as an object. {\sc OpenCyc} however precisely defines an
object as anything at least \emph{partially tangible}. This includes obviously
the humans, and actually many other entities that would not be commonly said to
be objects (the Earth for instance).\footnote{In such cases of discrepancy
between {\sc OpenCyc} concepts and human terminology, we manually label the {\sc
OpenCyc} concepts with appropriate human names: for instance, the OpenRobots
Ontology associates the label ``\emph{object}'' to the concept
\concept{cyc:Artifact} instead of the concept \concept{cyc:PartiallyTangible}.
These labels are used in priority during the grounding of verbal interactions.}
Thus the importance of relying on well-defined and standard semantics to
exchange information between artificial systems in a non-ambiguous way.

@@

\emph{Simplicity}: promotes plans that limit  too many interdependencies
between the actions of agents mentioned in the plan, as a problem with
executing just one of those actions could invalidate the entire
plan. Also intricate human-robot activity may cause discomfort since
the human will find himself repeatedly in a situation where his is
waiting for the robot to act,

@@

In the current implementation, the social rules are effectively
implemented by looking through all the plans produced and filtering
out the ones that do not meet the desired requirements. In the
future we intend to study algorithms that do such filtering online,
rather than after initial solutions are found.

@@

As HATP is a generic symbolic task planner and do not enforce any abstraction
level for the planning domain, we were able to design a domain built from
top-level tasks whose semantics are close to the one used in the human-robot
dialogue: the planner domain effectively contains concepts like \texttt{give},
\texttt{table}, \texttt{is on}. This leads to an effective mapping between the
knowledge extracted from the situation assessment or the dialogue, and the
planner.

@@

While parts of the architecture ({\sc Spark}, {\sc Oro}) have been deployed with
external execution controllers (like {\sc Cram}~\cite{Beetz2010} or the BERT
platform~\cite{Lallee2010b}, as reported in~\cite{Lemaignan2010}), we have also
developed dedicated robot controllers which integrate the whole stack introduced
in Figure~\ref{fig|archi}. {\sc Shary}~\cite{clodic2008shary} is the main one,
written in the \emph{Procedural Reasoning System} language~\cite{Ingrand1996}.
We have also developed the Python-based {\sc pyRobots}~\cite{lemaignan2015pyrobots} that
provides a large set of high-level actions and an event-based architecture well
suited for prototyping. They both rely on extensive integration with the knowledge
base, that serves as the primary source of semantics for the decision making process.

One of the main roles of {\sc Shary} is to control the production and execution
of shared plans. This means essentially context-based refinement and robot
actions execution, as well as monitoring of those achieved by its human
partner. One of the key design goal is to build such abilities in a generic
way, and to provide several levels of parametrisation allowing to adapt to
various environments, and various levels of involvement of the robot ranging
from teammate behaviour to assistant or proactive helper. Based on this,
the robot controller invokes the adequate human-aware planners and react to
events triggered by the {\sc Oro} knowledge base (as described below).

{\sc Shary}'s originality, as an execution control system, lies in its ability
to take into account not only the task achievement but also the communication
and monitoring needed to support interactive task
achievement~\cite{Rich1997,Sidner2005} in a flexible manner. {\sc Shary} allows
to bind action execution to \emph{communication policies} in order to produce
signals towards the human and to react to human actions. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through dialogue, by an
expressive motion or a combination of the two. It enables each agent to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference
mechanisms~\cite{fiore2014}. \fixme{Rachid, reviewer 2 asks for more details
about this process -> M. Fiore work?}

@@

The robot controller designer does not need to directly care about how this
\emph{desire} is produced (this is delegated to perception modules), he can
focus on the semantic of the desire.

@@

\subsubsection{Desires and Experiences}
\label{sect:desires}

@@

We present here elements of two of them in order to illustrate in a practical way
different aspects of the architecture.  The first one is focused on knowledge
representation and verbal interaction: the human asks for help to find and pack
objects ({\it Interactive Grounding I} in Table~\ref{table|experiments}). The
second one ({\it Cleaning the table}) involves the {\sc Shary} execution
controller and the HATP symbolic task planner. In this scenario, the human and
the robot try to cooperatively remove objects from a table, and behaviours and
motions are fully planned and then executed.

@@

The integration of these components in a consistent, working and observable
system builds upon the particular design of the interfaces between the
cognitive components: the information streams use high-level semantics,
represented as first-order logic statements. In that sense, our deliberative
architecture is similar to projects like {\sc cram}~\cite{Beetz2010} or PEIS
Ecology~\cite{saffiotti2005peis, daoutis2012cooperative}, with however a
stronger emphasize on the representation and interaction with humans. We
however distinguish ourselves from research on \emph{cognitive architectures}:
cognitive architectures are usually understood as an artificial yet principled
model of (human) cognition. While some have been deployed on autonomous robots,
like HAMMER~\cite{demiris2006hierarchical} or ACT-R/E~\cite{trafton2013act},
most are primarily concerned with the modeling of human cognition and are less
focused on practical deployment on socially interactive robots.

>>>>

Aligning the upper part of the ontology on {\sc OpenCyc} (as done by other
knowledge representation systems, like {\sc KnowRob}~\cite{Tenorth2009a} or PEIS
K\&R~\cite{daoutis2012cooperative}) has multiple advantages. First the design of
this part of the ontology is generally difficult: it pertains to abstract
concepts whose mutual relations comes to philosophical debates. The upper
taxonomy of {\sc OpenCyc} represents a relative consensus, at least within the
semantic Web community. Then, because it is a well established project with
numerous links to other on-line databases (like Wikipedia or WordNet), the reuse
of key {\sc OpenCyc} concepts ensures that the knowledge stored by the robot can
be shared or extended with well-defined semantics. The concept of \emph{Object}
represents a typical case of ambiguous meaning: in everyday conversation, an
object is a relatively small physical thing, that can be typically manipulated.
A human is not usually considered as an object. {\sc OpenCyc} however precisely
defines an object as anything at least \emph{partially tangible}. This includes
obviously the humans, and actually many other entities that would not be
commonly said to be objects (the Earth for instance).\footnote{In such cases of
discrepancy between {\sc OpenCyc} concepts and human terminology, we manually
label the {\sc OpenCyc} concepts with appropriate human names: for instance, the
OpenRobots Ontology associates the label ``\emph{object}'' to the concept
\concept{cyc:Artifact} instead of the concept \concept{cyc:PartiallyTangible}.
These labels are used in priority during the grounding of verbal interactions.}
Thus the importance of relying on well-defined and standard semantics to
exchange information between artificial systems in a non-ambiguous way.

@@

\emph{Simplicity}: promotes plans that limit as much as possible the interdependencies
between the actions of agents mentioned in the plan, as a problem with
executing just one of those actions could invalidate the entire
plan. Also intricate human-robot activity may cause discomfort since
the human will find himself repeatedly in a situation where his is
waiting for the robot to act,

@@

In the current implementation, the social rules are effectively
implemented as filters and that are applied whenever a plan is produced.
In the future we intend to extend the plan-search algorithm and integrate the social rules 
in the process itself.

@@

As HATP is a generic symbolic task planner and does not enforce any abstraction
level for the planning domain, we were able to design a domain built from
top-level tasks whose semantics are close to the one used in the human-robot
dialogue: the planner domain effectively contains concepts like \texttt{give},
\texttt{table}, \texttt{is on}. This leads to an effective mapping between the
knowledge extracted from the situation assessment or the dialogue, and the
planner.

@@

While parts of the architecture ({\sc Spark}, {\sc Oro}) have been deployed with
external execution controllers (like {\sc Cram}~\cite{Beetz2010} or the BERT
platform~\cite{Lallee2010b}, as reported in~\cite{Lemaignan2010}), we have also
developed dedicated robot controllers which integrate the whole stack introduced
in Figure~\ref{fig|archi}. {\sc Shary}~\cite{clodic2008shary} is the main one,
written in the \emph{Procedural Reasoning System (PRS)} language~\cite{Ingrand1996}.
We have also developed the Python-based {\sc pyRobots}~\cite{lemaignan2015pyrobots} that
provides a large set of high-level actions and an event-based architecture well
suited for prototyping. They both rely on extensive integration with the knowledge
base, that serves as the primary source of semantics for the decision making process.

One of the main roles of {\sc Shary} is to control the production and execution
of shared plans. This means essentially context-based refinement and robot
actions execution, as well as monitoring of those achieved by its human
partner. One of the key design goals is to build such abilities in a generic
way, and to provide several levels of parametrisation allowing to adapt to
various environments, and various levels of involvement of the robot ranging
from teammate behaviour to assistant or proactive helper. Based on this,
the robot controller invokes the adequate human-aware planners and react to
events triggered by the {\sc Oro} knowledge base (as described below).

{\sc Shary}'s originality, as an execution control system, lies in its ability
to take into account not only the task achievement but also the communication
and monitoring acts needed to support human-robot interactive task
achievement~\cite{Rich1997,Sidner2005} in a flexible manner. {\sc Shary} allows
to bind action execution to \emph{communication policies} in order to produce
signals towards the human and to react to human actions. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through dialogue, by an
expressive motion or a combination of the two. It enables each agent to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference
mechanisms~\cite{fiore2014}. \fixme{Rachid, reviewer 2 asks for more details
about this process -> M. Fiore work?}

@@

The robot controller designer does not need to directly care about how this
\emph{desire} is produced (this is delegated to perception modules), he can
focus on the semantics of the desire.

@@

\subsubsection{Complying with Human Desires and Experiences}
\label{sect:desires}

@@

We present here elements of two of them in order to illustrate in a practical way
different aspects of the architecture.  The first one is focused on knowledge
representation and verbal interaction: the human asks for help to find and pack
objects ({\it Interactive Grounding I} in Table~\ref{table|experiments}). The
second one ({\it Cleaning the table}) involves the {\sc Shary} execution
controller and the HATP symbolic task planner. In this scenario, the human and
the robot are in a situation when they need to cooperatively remove objects from a table, and behaviours and
motions are fully planned and then executed.

@@

The integration of these components in a consistent, working and observable
system builds upon the particular design of the interfaces between the cognitive
components: the information streams use high-level semantics, represented as
first-order logic statements. In that sense, our deliberative architecture is
similar to projects like {\sc cram}~\cite{Beetz2010}, KeJia~\cite{Chen2010} or
PEIS Ecology~\cite{saffiotti2005peis, daoutis2012cooperative}, with however a
stronger emphasize on the representation and interaction with humans. We however
distinguish ourselves from research on \emph{cognitive architectures}: cognitive
architectures are usually understood as an artificial yet principled model of
(human) cognition. While some have been deployed on autonomous robots, like
HAMMER~\cite{demiris2006hierarchical} or ACT-R/E~\cite{trafton2013act}, most are
primarily concerned with the modeling of human cognition and are less focused on
practical deployment on socially interactive robots.
